---
title: "GLM-semantic-judgement"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r}
library(ggplot2)
library(dplyr)
library(nnet)
library(dobson)
library(viridis)
library(stargazer)
library(lme4)
library(lmerTest)
library(readxl)
library(jtools)
library(dplyr)
library(brms)
library(bayesplot)
library(future)
plan("multisession")
options(mc.cores = 3)

library(bayestestR)



```

```{r}
data_semantics <- read.csv(file = 'semantic_judgement20p.csv', header = TRUE)
data_semantics$layer <- factor(data_semantics$layer, levels = c("layer9-17", "layer0-5", "layer6-8"))
data_semantics$Source.target.pair <- factor(data_semantics$Source.target.pair, levels = c("OO", "TT", "OT"))

## Rename the layers
levels(data_semantics$layer) <- list( Later = "layer9-17", Early = "layer0-5", Middle = "layer6-8")

attribute_level <- c("Lighting", "Shape/Orientation", "Material", "Color")
data_semantics$response <- factor(data_semantics$response, levels = attribute_level)

levels(data_semantics$response)

num_people <- 20
id <- rep(1:num_people,each=450)
data_semantics$id <- factor(id)
```


see: https://calogica.com/r/rstan/2020/07/05/season-pass-hierarchical-modelng-r-stan-brms.html
```{r}
model <- brm(response~layer*Source.target.pair + 
                            (1| id),
                          data = data_semantics,
                          family = "categorical",
                          iter = 8000, 
                          chains = 3,
                          cores = 3)

save(model, file = "semantic_brms.RData")

model_prior <- brm(response~layer*Source.target.pair + 
                            (1| id),
                          data = data_semantics,
                          family = "categorical",
                          prior = set_prior("normal(0,1)", class = "b"),
                          iter = 8000, 
                          chains = 3,
                          cores = 3)

save(model_prior, file = "semantic_brms_normal_0_1.RData")


model_norm10 <- brm(response~layer*Source.target.pair + 
                            (1| id),
                          data = data_semantics,
                          family = "categorical",
                          prior = set_prior("normal(0,10)", class = "b"),
                          iter = 8000, 
                          chains = 3,
                          cores = 3)

save(model_norm10, file = "semantic_brms_normal_0_10.RData")


model_uniform <- brm(response~layer*Source.target.pair + 
                            (1| id),
                          data = data_semantics,
                          family = "categorical",
                          prior = set_prior("uniform(0,1)", class = "b"),
                          iter = 8000, 
                          chains = 3,
                          cores = 3)

save(model_uniform, file = "semantic_brms_uniform_0_1.RData")
```


create tidy data
```{r}

output<-broom.mixed::tidy(model, conf.int = TRUE, conf.level=.95,conf.method = c("quantile", "HPDinterval"), effects = 'fixed')

output
```


```{r}
library(xtable)
xtable(output)

# & Mean Est & Est.Error & HDI Lower & HDI Upper
```


Quick plot of the parameter estimates (Posterior intervals)
```{r}
mcmc_plot(model)
```

posterior distributions
```{r}
mcmc_plot(model, pars = "^b_", type = "hist")
```

using the builtin RStan capabilities to check mixing of the parameters
```{r}
mcmc_plot(model, pars = "^b_", type = "trace")
```

Diagnostic plots
```{r}
mcmc_plot(model, type = "neff")
mcmc_plot(model, type = "rhat")
```

Acceptance and divergence plots
```{r}
mcmc_plot(model, type = "nuts_acceptance")
mcmc_plot(model, type = "nuts_divergence")
```

We will then look at the summary statistics
```{r}
summary(model)
```
*Note* we want Rhat to at or very close to 1 for convergence

Run a leave one out assessment
```{r}
loo(model)
```

Plot the loo results
```{r}
plot(loo(model))
```

Visualize the parameters
```{r}
plot(model, pars="^b")
```

Run a predictive probability check
```{r}
pp2 <- brms::pp_check(model)
pp2 + theme_bw()
```

Assess the conditional effects of the model
```{r}
plot(conditional_effects(model, categorical = TRUE), ask = F)
```

```{r}
rope(model_prior, range = c(-.1,.1), ci = .95, effects = "fixed")
```

```{r}
prior_summary(model_prior, all =TRUE)

stancode(model)
```


https://bookdown.org/ajkurz/Statistical_Rethinking_recoded/interactions.html
```{r}
conditions <- data.frame(layer = c("Early", "Middle", "Later"))
conditions2 <- data.frame(Source.target.pair = c("TT", "OO", "OT"))
conditional_effects(model, categorical=TRUE, conditions = c(conditions,conditions2))
```
when source target pair is X axis
1 is early
2 is middle
3 is later

```{r}
conditions2 <- data.frame(Source.target.pair = c("OT", "OO", "TT"))
p <- conditional_effects(model, categorical=TRUE, conditions = conditions2)[[1]]
p$Source.target.pair <- factor(p$Source.target.pair, levels=c("OT", "OO", "TT"))

ggplot(p) + aes(
   x = factor(layer, level = c( "Early", "Middle", "Later")),
   y = estimate__,
   colour = effect2__
  ) + facet_wrap(~Source.target.pair, ncol = 3) + 
  geom_point(position = position_dodge(width = 0.5), size = 3) +
  geom_errorbar(aes(ymin=lower__, ymax=upper__), width=0.5,
                position = position_dodge(width = 0.5)) +
  xlab("Layer-manipulation") +
  ylab("Estimated probability") +
  labs(color='Scene attribute') +
  theme_bw()

```


```{r}
conditional_effects(model, categorical=TRUE, conditions = conditions2)
```


turn off scientific notation
```{r}
options(scipen=999)
```

```{r}
mcmc_areas(
    model,
    regex_pars = "b_",
    prob = 0.95, 
    point_est = "median",
    area_method = "equal height"
    ) +
    geom_vline(xintercept = 0, color = "red", alpha = 0.6, lwd = .8, linetype = "dashed") 
```

get relative risk
Please note that:
est is the posterior mean, se is actually the sd of the posterior

```{r}
round(exp(fixef(model)),2)
```

https://cran.r-project.org/web/packages/brms/vignettes/brms_multilevel.pdf

## Extract table for LaTEX
```{r}
table <- xtable(round(exp(fixef(model_prior)),2))
table
```

```{r}
summary(model_prior)  # group level effect. not exponentiated
table2 <- xtable(round(exp(ranef(model)),2))
```


look at the siny diagnostic app
```{r}
shinystan::launch_shinystan(model)
```

Good for main effects
```{r}
plot(conditional_effects(model, conditions = "layer:Source.target.pair",categorical=T))
```




Try to knit
```{r}
library(texreg)
#knitreg(model, center=FALSE, caption = "test", table = TRUE)
```
```{r}
load("data_brms.RData")
```


tester code:
- no valid effects found
```{r}
int_conditions <- list(Source.target.pair = c("TT", "OO", "OT"))
  
conditions <- data.frame(layer=c("Early", "Middle", "Later"))
conditional_effects(model, categorical=TRUE, 
                    effects = "layer:Source.target.pair",
                    int_conditions = int_conditions)
```


```{r}
cond <- make_conditions(model, "layer")
conditional_effects(model, categorical=TRUE, 
                    effects = "layer:Source.target.pair",
                    int_conditions = cond)
```

https://psyarxiv.com/cdxv3/download

https://michael-franke.github.io/bayes_mixed_regression_tutorial/faintr/doc/faintr_basics.html

load functions from faintr package (manually created a function source file as the package is not working right)
```{r}
#source("helper functions.R")

#post_cells(model)$predictor_values
```
issue - only works with gaussian models.


marginal effects
```{r}
sjPlot::plot_model(model)
```

```{r}
plot(conditional_effects(model, categorical = T))
```